Individualized Measures of Partisan Fairness and Utility in Redistricting (??)

### 2021-08-30 paper/paper.Rmd
mini schematic

@@

# Voter Utility in Election Outcomes

The utility voters gain from a particular election outcome naturally varies across the electorate, depending on factors such as political engagement, partisanship, race and ethnicity, individual policy preferences, individual candidate attributes, and more.
Here, we restrict our attention to what we believe are the two dominant contributors to partisan utility: which party represents a voter's district, and how many overall seats a voter's preferred party wins.

@@

```{=tex}
\begin{restatable}{prop}{propglobal} \label{prop:global}
Let $S=\{s_p:p\in P\}$ be a set of party popular vote shares, and $f:[0,1]\bijto[0,1]$ be a rule for assigning each party a share of seats according to their share of the popular vote.
Define the total utility for this rule as \[
    U_e^{(G)}(f) = \sum_{v\in V} h\qty(f\qty(s_{\vote_e(v)})).
\] 
Then if $h$ is convex, $U_e^{(G)}$ is maximized for $f(x)=\ind\{x\ge \max S\}$, and if $h$ is concave, the maximizer of $U_e^{(G)}$ will be an increasing function.
In particular, if $h(x)=\log(x)$ and every party receives at least one vote, then $f(x)=x$ maximizes $U_e^{(G)}$.

@@

# Towards Individualized Representational Harm

@@

# Measures of Individual Injury

@@

# Discussion

>>>>

```{r SETUP, include=FALSE}
library(knitr)
library(here)

opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE,
               fig.path=here("paper/figures/"), fig.align="center",
               fig.width=(8.5-2*1)/2, out.width="100%", fig.asp=0.8)
```

@@

## Running Examples

To illustrate the notation and measures we introduce, this article will make use of three running examples, which are stylized representations of U.S. states: Mininois, Minissouri, and Minichussets.
Mininois has one large Democratic city which can electorally dominate the rest of the state; Minissouri has two medium-sized cities which are not large enough to deliver a statewide Democratic majority; and Minichusetts has a uniform 3--2 Democratic split in every precinct.
Schematics for these examples are shown in Figure \ref{fig:mini-schematic}.

```{r mini-schematic, fig.cap="Schematic maps of the three running examples, showing the partisan composition of each of the 36 precincts. The total voting population for each example is 180."}
include_graphics(here("paper/figures/minis_schematic.pdf"))
```

## Outline of the Paper

Section \ref{sec:voter-util} provides the necessary notation and introduces our measures of voter utility.
Section \ref{sec:indiv-harm} builds a measure of individual harm from this notion of utility.
Section \ref{sec:empirical} applies this measure to a real-world example.
Section \ref{sec:discussion} concludes.

# Voter Utility in Election Outcomes {#sec:voter-util}

The utility voters gain from a particular election outcome naturally varies across the electorate, depending on factors such as political engagement, partisanship, race and ethnicity, individual policy preferences, and individual candidate attributes.
Here, we restrict our attention to what we believe are the two dominant contributors to partisan utility: which party represents a voter's district, and how many overall seats a voter's preferred party wins.

@@

```{=tex}
\begin{restatable}{prop}{propglobal} \label{prop:global}
Let $S=\{s_p:p\in P\}$ be a set of party popular vote shares, and $f:[0,1]\bijto[0,1]$ be a rule for assigning each party a share of seats according to their share of the popular vote.
Define the total utility for this rule as \[
    U_e^{(G)}(f) = \sum_{v\in V} h\qty(f\qty(s_{\vote_e(v)})).
\] 
Then if $h$ is convex, $U_e^{(G)}$ is maximized for $f(x)=\ind\{x\ge \max S\}$, and if $h$ is strictly concave, the maximizer of $U_e^{(G)}$ will be a strictly increasing function.
In particular, if $h(x)=\log(x)$ and every party receives at least one vote, then $f(x)=x$ maximizes $U_e^{(G)}$.

@@

# Towards Individualized Representational Harm {#sec:indiv-harm}

@@

@@

# Real-world Example {#sec:empirical}

# Discussion {#sec:discussion}
